Disclosure of Product System Models in Life Cycle Assessment: Achieving Transparency and Privacy

### 2017-11-20 aggregation/publication-example.tex
Correct column numbers

Ecoinvent version 3 is provided in three different system models that reflect different linking strategies.  The example is drawn from the ``Allocation at the point of substitution'' or APOS model, which includes 11,420 processes that produce 12,966 product flows.  Of these, 10,282 are background flows and the rest are foreground flows.

The example system reports production of organic potatoes supplied to the global market (Table \ref{table:potato}).  The foreground includes nine nodes, of which six (nodes 3 through 8) form a cyclic dependency associated with the production of potato seeds.  The Ecoinvent database's use of ``markets'' as mixer processes is evident in the table: node 0 is a mixer process that combines Swiss (``CH'') production (node 1) weighted at 2.4\%  with rest-of-World (``RoW'') production (node 2) weighted at 97.6\%.  That same market split (2.4 / 97.6) can also be seen in nodes 7 and 8.

Nodes 4 and 5, which make seeds ready ``for setting,'' are mixed by node 8. Although nodes 4 and 5 are geographically distinguished (CH vs RoW), both can be seen to consume potato seed from the global market.

Looking at the dependency and emission lists, the different ``signatures'' of different kinds of processes can be seen: nodes 1, 2, 3, and 6 are clearly agricultural processes that require irrigation, tillage, manure and so on.  Nodes 0 and 7 are visible as market processes, their only requirements being transport processes.  Nodes 4 and 5 each consume electricity and require use of a ``multi-storey building.''  Taken together, the CH-locality processes appear to use CH irrigation and electricity supply but are otherwise similar to their RoW counterparts.  The product model includes no cutoff flows.

>>>>

Ecoinvent version 3 is provided in three different system models that reflect different linking strategies.  The example is drawn from the ``Allocation at the point of substitution'' or APOS model of Ecoinvent 3.2, which includes 11,420 processes that produce 12,966 product flows.  Of these, 10,282 are background flows and the rest are foreground flows.

The example system reports production of organic potatoes supplied to the global market (Figure \ref{table:potato}).  The foreground includes nine nodes, of which six (nodes 3 through 8) contain cyclic dependencies associated with the production of potato seeds.  The Ecoinvent database's use of ``markets'' as mixer processes is evident in the table: node 0 is a mixer process that combines Swiss (``CH'') production (node 1) weighted at 2.4\%  with rest-of-World (``RoW'') production (node 2) weighted at 97.6\%.  That same market split (2.4 / 97.6) can also be seen in nodes 4 and 8.

Nodes 5 and 6, which make seeds ready ``for setting,'' are mixed by node 8. Although nodes 5 and 6 are geographically distinguished (CH vs RoW), both can be seen to consume potato seed from the global market.

Looking at the dependency and emission lists, the different ``signatures'' of different kinds of processes can be seen: nodes 1, 2, 3, and 7 are clearly agricultural processes that require irrigation, tillage, manure and so on.  Nodes 0 and 4 are visible as market processes, their only requirements being transport processes.  Nodes 5 and 6 each consume electricity and require use of a ``multi-storey building.''  Taken together, the CH-locality processes appear to use CH irrigation and electricity supply but are otherwise similar to their RoW counterparts.  The product model includes no cutoff flows.
